1638 / 1.1

### 2023-10-02 work/oct-23/draft-tab.tex
add to work/oct-23
draft and draft-tab tex files had additions and possible subtractions during copy editing

\begin{table}[h]% \centering not needed for amsart documentclass
\caption{Series which would prove useful in version 1.0.0 or a later version.}% must top table for amsart
\label{t:series}% should follow caption for amsart
\begin{tabularx}{\textwidth}{lScL}
\toprule
series & of & 1.0.0 & note\\
\midrule
calendar & records in significant or major collections & yes & Known major records collections include some in the AGI, ARS, TNA. Noted calendars include Burdon's \titleit{Archives}, the \titleit{CSP}, the \titleit{CDI}.\\
calendar & records in minor collections & no & Various identified in historical literature and version 0.n.0. Some catalogued. Noted calendars include \emph{some} of the Camden Series.\\
calendar & rare literature & no & Rare literature includes rare books, scarce periodicals. Noted calendars include \emph{some} of the Camden Series.\\
catalogue & historical literature & yes & Noted catalogues include xx.\\
catalogue & non-historical literature & no & Non-historical literature includes eg archaeological, geographical literature. Noted catalogues include xx.\\
catalogue & official literature & no & Official literature includes eg Crown reports, parliamentary papers. Noted catalogues include xx.\\
catalogue & non-official literature & no & Non-official literature includes eg press. Noted catalogues include xx.\\
catalogue & manuscripts & yes & Noted catalogues include xx.\\
chronicle & pre-Columbian events & may & Noted chronicles include xx.\\
chronicle & Columbian events & yes & Noted chronicles include xx.\\
compendium & pre-statistical or historical statistics & yes & Noted compendia include the \titleit{BHS}, the \titleit{HSUS}.\\
compendium & statistical or modern statistics & yes & Noted compendia include xx.%for modern as in 19th to 20th cent
\\
dictionary & identities of natural persons & may & Noted dictionaries include Oxford's \titleit{DNB}, the RAH's \titleit{DBE}.\\
dictionary & identities of non-natural persons & no & Noted dictionaries include xx.\\
gazetteer & identities of natural points or shapes & no & Noted gazetteers include Enciso's \titleit{Suma de Geographia}.\\
gazetteer & identities of non-natural points or shapes & may & Noted gazetteers include xx.\\
\bottomrule
\addlinespace[\belowrulesep]% suggested by booktabs package
\multicolumn{4}{p{\textwidth}}{\tabnote{Header row---\mention{1.0.0} is version 1.0.0. First column---\mention{calendar} includes \emph{both} those which describe or summarise items or their contents \emph{and} those which further transcribe or translate their contents; \mention{catalogue} includes bibliographies and the like; \mention{compendium} includes statistical series, digests, and the like; \mention{dictionary} includes directories and the like; \mention{gazetteer} includes geographical dictionaries, pilots, maps, atlases, and the like. Second column---append `of use to historical reasoning' to all entries, and read \mention{literature} as publications. Third column---\mention{may} is maybe or perhaps. Fourth column---\mention{notable} as in relatively salient to the author during the building of version 0.n.0.}}
\end{tabularx}
\end{table}

>>>>

\begin{table}[h]% \centering not needed for amsart documentclass
\caption{Series which would prove useful in version 1.0.0 or a later version.}% must top table for amsart
\label{t:series}% should follow caption for amsart
\begin{tabularx}{\textwidth}{lScL}
\toprule
series & of & 1.0.0 & note\\
\midrule
calendar & records in significant or major collections & yes & Known major records collections include some in the AGI, ARS, TNA. Noted calendars include Burdon's \titleit{Archives}, the \titleit{CSP}, the \titleit{CDI}.\\
calendar & records in minor collections & no & Various identified in historical literature and version 0.n.0. Some catalogued. Noted calendars include \emph{some} of the Camden Series.\\
calendar & rare literature & no & Rare literature includes rare books, scarce periodicals. Noted calendars include \emph{some} of the Camden Series.\\
calendar & oral history & no & Noted calendars include xx.\\
catalogue & historical literature & yes & Noted catalogues include xx.\\
catalogue & non-historical literature & no & Non-historical literature includes eg archaeological, geographical literature. Noted catalogues include xx.\\
catalogue & official literature & no & Official literature includes eg Crown reports, parliamentary papers. Noted catalogues include xx.\\
catalogue & non-official literature & no & Non-official literature includes eg press. Noted catalogues include xx.\\
catalogue & manuscripts & yes & Noted catalogues include xx.\\
chronicle & pre-Columbian events & may & Noted chronicles include xx.\\
chronicle & Columbian events & yes & Noted chronicles include xx.\\
compendium & pre-statistical or historical statistics & yes & Noted compendia include the \titleit{BHS}, the \titleit{HSUS}.\\
compendium & statistical or modern statistics & yes & Noted compendia include xx.%for modern as in 19th to 20th cent
\\
dictionary & identities of natural persons & may & Noted dictionaries include Oxford's \titleit{DNB}, the RAH's \titleit{DBE}.\\
dictionary & identities of non-natural persons & no & Noted dictionaries include xx.\\
gazetteer & identities of natural points or shapes & no & Noted gazetteers include Enciso's \titleit{Suma de Geographia}.\\
gazetteer & identities of non-natural points or shapes & may & Noted gazetteers include xx.\\
\bottomrule
\addlinespace[\belowrulesep]% suggested by booktabs package
\multicolumn{4}{p{\textwidth}}{\tabnote{Header row---\mention{1.0.0} is version 1.0.0. First column---\mention{calendar} includes \emph{both} those which describe or summarise items or their contents \emph{and} those which further transcribe or translate their contents; \mention{catalogue} includes bibliographies and the like; \mention{compendium} includes statistical series, digests, and the like; \mention{dictionary} includes directories and the like; \mention{gazetteer} includes geographical dictionaries, pilots, maps, atlases, and the like. Second column---append `of use to historical reasoning' to all entries, and read \mention{literature} as publications. Third column---\mention{may} is maybe or perhaps. Fourth column---\mention{notable} as in relatively salient to the author during the building of version 0.n.0.}}
\end{tabularx}
\end{table}
